Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-05 paper/main.tex
place figures freely
add todo

\begin{figure}[H]
    \centering
    % \includegraphics[width=0.8\textwidth]{overview.pdf}
    \includestandalone[width=0.8\textwidth]{figures/concept/overview}
    \caption{
        The project can be divided into subcomponents (yellow, red) that interact with and depend on
        each other.
        Yellow blocks are provided by this work and red blocks require additional input such as
        modeling assumptions or data.
        Blue blocks indicate possible future extensions of this project.
        Every component implicitly builds on the spatial representation of rod-shaped bacteria as
        vertices $\vec{x}_i$.
    }
    \label{fig:flowchart-project-structure}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{docs/source/_static/mechanics.png}
    \caption{
        Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ have been exaggerated such that they can be identified more easily.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with $0$ curvature.
    }
    \label{fig:mechanics-bacterium}
\end{figure}

@@

\begin{figure}[H]
    \centering
    % \begin{tikzonimage}[width=0.9\textwidth]{visualization.pdf}
    %     \node at (0.025, 0.975)[anchor=north west, rectangle, draw, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    % \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/raw_pv/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/masks/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/images/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        (A) shows the result from combining sphere and cylinder meshes to obtain the shape of a
        bacterial rod.
        This render contains lighting coming from 2 light sources which thus produces a small glow
        on the upper part of the meshes.
        (B) Unique color values are assigned to each agent and light sources are removed.
        Afterwards, the image is rendered by projecting along the z-axis.
        (C) We use physically-based rendering and assign properties such as roughness and
        reflectivity to generate an initial render.
        Afterwards, we apply white noise to the pixel values of image.
        In the future, we hope to extend this approach in order to construct near-realistic
        microscopic images from synthetic data.
    }
    \label{fig:progression-image-generation}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.36\textwidth]
        {docs/source/_static/fitting-methods/algorithm/image001042.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.36\textwidth]
        {docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.255\textwidth]
        {docs/source/_static/fitting-methods/algorithm/interpolate-positions.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        (A) Input image.
        (B) Result of the skeletonization algorithm for a single cell.
        (C) Vertices $\vec{x}_i$ which have been interpolated from the skeletonized cell.
        They represent the position of our cell-agents.
    }
    \label{fig:position-extraction-algorithm}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Progression of generated masks with estimated and exact positions.
        Comparison of masks across generations. Compare estimated with exact rod lengths.
"Iceberg plot"
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{minipage}{0.5\textwidth}
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-1.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-2.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \linebreak
    \vspace{0.01\textwidth}
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-3.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-4.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}
    \end{minipage}%
    \begin{minipage}{0.49\textwidth}
        \begin{tikzonimage}[width=\textwidth]
            {docs/source/_static/fitting-methods/penalty-time-flow.png}%
            \node at (0, 0.975)[anchor=north west, draw, rectangle, minimum width=15pt, minimum height=15pt]{\textbf{E}};
        \end{tikzonimage}
    \end{minipage}
    \caption{
        The figure shows two masks (A,B) which will be compared against each other.
        Image (B) contains more cells which are a result of cellular division events that have not
        yet occurred in image (A).
        (C) "Naive" comparison of cell masks, which identifies pixels of non-matching colors and
        assigns a loss by counting these pixels.
        This simple approach does not take into consideration the parental relationship.
        This approach is displayed in (D) where pixels of cells that are directly related have been
        colored in gray.\\
        (E) Comparison of loss functions, exponential regression (ER) and number of cells.
        % Total loss between successive iteration steps $t_n,t_{n+1}$.
        The overall shape of the loss is expected to have the slope of an exponential function.
        We can clearly see that division events introduce jumps within this relationship.
        In the case where we account for the parental relationship, these jumps are mitigated.
        The loss value was set to $0$ for pixel-comparisons which belong to cells that are in a
        parental relationship.
    }
    \label{fig:mask-difference-metric}
\end{figure}

@@

\label{subsec:parameter-estimation-individual-treatment}
\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-individual.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-average.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/parameter-distribution.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \caption{
        % TODO use same y-axis across the plots
        (A) The subfigure shows the time-evolution of the rod-lengths for every individual
        bacterium.
        These growth curves are fitted individually with delayed exponential function.
        (B) The datapoints are created by averaging the rod-lengths shown in subfigure (A) and then
        fitted with an exponential function.
        The uncertainty band is the standard deviation of the averaged datapoints.
        (C) Blue dots show the combination of estimated growth rates and delays for individual
        bacteria while the orange dot corresponds to the average.
        Ellipses around the datapoints are taken from the uncertainty of the fits.
        Time is given in units of frames of the movie from which the data have been extracted.
    }
    \label{fig:estimated-growth-rates}
\end{figure}

% --------------------------------------------------------------------------------------------------
\subsection{Without Division}
For now, we will focus on a time-interval which does not contain any division events.
By doing so, we can utilize the simpler and more performant position comparison scheme for our loss
function.
For this dataset, we assumed that all interaction parameters which specify the interaction
potential are identical across all agents but growth rates and the physical radii of the cells are
individual and we optimize them like any other global parameter.
We chose to optimize for 3 interaction parameters of the Mie potential $n,m,V_0$ and two parameters
which were individual for each cell, namely the radii $r_i$ and growth rates $\mu_i$.
We also included the damping constant $\lambda$ and removed any stochastic motion contributions
($D=0$).
This leads to a total of $4+2\times 6=16$ parameters.
To estimate these parameters we used a latin-hypercube~\cite{McKay1979} sweep across the parameter
space and performed a local minimization with the Nelder-Mead~\cite{Powell1973} method.

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.54\textwidth]
        {figures/crm_fit/snapshots/predicted-031111.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.41\textwidth]
        {figures/crm_fit/celldifss/cell-031111.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO do we need this figure?}
        (A) A microscopic image with the predicted positions of the cells overlayed on top.
        (B) Differences between extracted and predicted positions.
        % TODO make this figure to scale
    }
    \label{fig:celldiffs-individual}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/damping.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-m.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-n.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/strength.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-0.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}
    \caption{
        Sensitivity analyses werer performed for every optimized parameter of our model.
        (A-F) show the curves of loss functions when varying this respective parameter and keeping
        all others constant at the value of the found optimum (blue dot).
        In the cases of (B-F), we can see that a minimum was achieved and thus the parameters could
        be estimated.
        However, for the case of the damping constant $\lambda$ in (A), we see that the upper bound
        is open.
        This suggests that our model could be reduced with regard to this parameter.
        We have exemplified the values for radii $r_i$ and growth rates $\mu_i$ with values of the
        first cell.
        The remaining plots can be found in the supplementary material in
        section~\ref{sec:supplement-parameter-profiles}.
    }
    \label{fig:parameter-estimates-single-step}
\end{figure}

@@

%###################################################################################################
% EXCLUDE THIS FOR NOW
% \section{Plastic Deformations}
% 
% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/0000000023.png}\\
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/angles.pdf}
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/endpoints.pdf}
%     \caption{TODO}
%     \label{fig:amir}
% \end{figure}

@@

%###################################################################################################
\section{Parameter Estimation}
\label{sec:supplement-parameter-profiles}
%TODO {explain profiles}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-5.pdf}
    \caption{Parameter estimation of growth rates for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement-growth-rates}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-5.pdf}%
    \caption{Parameter estimation of radii for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement-radii}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.49\textwidth]
        {docs/source/_static/performance/computation-time-with-initial-agents.pdf}
    \includegraphics[width=0.49\textwidth]{docs/source/_static/performance/flamegraph.pdf}
    \caption{TODO}
    \label{fig:performance}
\end{figure}

>>>>

\begin{figure}
    \centering
    % \includegraphics[width=0.8\textwidth]{overview.pdf}
    \includestandalone[width=0.8\textwidth]{figures/concept/overview}
    \caption{
        The project can be divided into subcomponents (yellow, red) that interact with and depend on
        each other.
        Yellow blocks are provided by this work and red blocks require additional input such as
        modeling assumptions or data.
        Blue blocks indicate possible future extensions of this project.
        Every component implicitly builds on the spatial representation of rod-shaped bacteria as
        vertices $\vec{x}_i$.
    }
    \label{fig:flowchart-project-structure}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{docs/source/_static/mechanics.png}
    \caption{
        Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ have been exaggerated such that they can be identified more easily.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with $0$ curvature.
    }
    \label{fig:mechanics-bacterium}
\end{figure}

@@

\begin{figure}
    \centering
    % \begin{tikzonimage}[width=0.9\textwidth]{visualization.pdf}
    %     \node at (0.025, 0.975)[anchor=north west, rectangle, draw, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    % \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/raw_pv/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/masks/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/images/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        (A) shows the result from combining sphere and cylinder meshes to obtain the shape of a
        bacterial rod.
        This render contains lighting coming from 2 light sources which thus produces a small glow
        on the upper part of the meshes.
        (B) Unique color values are assigned to each agent and light sources are removed.
        Afterwards, the image is rendered by projecting along the z-axis.
        (C) We use physically-based rendering and assign properties such as roughness and
        reflectivity to generate an initial render.
        Afterwards, we apply white noise to the pixel values of image.
        In the future, we hope to extend this approach in order to construct near-realistic
        microscopic images from synthetic data.
    }
    \label{fig:progression-image-generation}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.36\textwidth]
        {docs/source/_static/fitting-methods/algorithm/image001042.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.36\textwidth]
        {docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.255\textwidth]
        {docs/source/_static/fitting-methods/algorithm/interpolate-positions.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        (A) Input image.
        (B) Result of the skeletonization algorithm for a single cell.
        (C) Vertices $\vec{x}_i$ which have been interpolated from the skeletonized cell.
        They represent the position of our cell-agents.
    }
    \label{fig:position-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Progression of generated masks with estimated and exact positions.
        Comparison of masks across generations. Compare estimated with exact rod lengths.
"Iceberg plot"
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-1.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-2.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \linebreak
    \vspace{0.01\textwidth}
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-3.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.48\textwidth]
        {docs/source/_static/fitting-methods/progressions-4.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}
    \end{minipage}%
    \begin{minipage}{0.49\textwidth}
        \begin{tikzonimage}[width=\textwidth]
            {docs/source/_static/fitting-methods/penalty-time-flow.png}%
            \node at (0, 0.975)[anchor=north west, draw, rectangle, minimum width=15pt, minimum height=15pt]{\textbf{E}};
        \end{tikzonimage}
    \end{minipage}
    \caption{
        The figure shows two masks (A,B) which will be compared against each other.
        Image (B) contains more cells which are a result of cellular division events that have not
        yet occurred in image (A).
        (C) "Naive" comparison of cell masks, which identifies pixels of non-matching colors and
        assigns a loss by counting these pixels.
        This simple approach does not take into consideration the parental relationship.
        This approach is displayed in (D) where pixels of cells that are directly related have been
        colored in gray.\\
        (E) Comparison of loss functions, exponential regression (ER) and number of cells.
        % Total loss between successive iteration steps $t_n,t_{n+1}$.
        The overall shape of the loss is expected to have the slope of an exponential function.
        We can clearly see that division events introduce jumps within this relationship.
        In the case where we account for the parental relationship, these jumps are mitigated.
        The loss value was set to $0$ for pixel-comparisons which belong to cells that are in a
        parental relationship.
    }
    \label{fig:mask-difference-metric}
\end{figure}

@@

\label{subsec:parameter-estimation-individual-treatment}
\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-individual.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-average.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/parameter-distribution.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \caption{
        % TODO use same y-axis across the plots
        (A) The subfigure shows the time-evolution of the rod-lengths for every individual
        bacterium.
        These growth curves are fitted individually with delayed exponential function.
        (B) The datapoints are created by averaging the rod-lengths shown in subfigure (A) and then
        fitted with an exponential function.
        The uncertainty band is the standard deviation of the averaged datapoints.
        (C) Blue dots show the combination of estimated growth rates and delays for individual
        bacteria while the orange dot corresponds to the average.
        Ellipses around the datapoints are taken from the uncertainty of the fits.
        Time is given in units of frames of the movie from which the data have been extracted.
    }
    \label{fig:estimated-growth-rates}
\end{figure}

% --------------------------------------------------------------------------------------------------
\subsection{Without Division}
For now, we will focus on a time-interval which does not contain any division events.
By doing so, we can utilize the simpler and more performant position comparison scheme for our loss
function.
For this dataset, we assumed that all parameters which specify the interaction potential are
identical across all agents but growth rates \textbf{TODO check this} and the physical radii of the
cells are individual and we optimize them like any other global parameter.
We chose to optimize for 3 interaction parameters of the Mie potential $n,m,V_0$ and two parameters
which were individual for each cell, namely the radii $r_i$ and growth rates $\mu_i$.
We also included the damping constant $\lambda$ and removed any stochastic motion contributions
($D=0$).
This leads to a total of $4+2\times 6=16$ parameters.
To estimate these parameters we used a latin-hypercube~\cite{McKay1979} sweep across the parameter
space and performed a local minimization with the Nelder-Mead~\cite{Powell1973} method.

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.54\textwidth]
        {figures/crm_fit/snapshots/predicted-031111.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.41\textwidth]
        {figures/crm_fit/celldifss/cell-031111.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO do we need this figure?}
        (A) A microscopic image with the predicted positions of the cells overlayed on top.
        (B) Differences between extracted and predicted positions.
        % TODO make this figure to scale
    }
    \label{fig:celldiffs-individual}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/damping.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-m.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/exponent-n.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/strength.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-0.pdf}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}
    \caption{
        Sensitivity analyses werer performed for every optimized parameter of our model.
        (A-F) show the curves of loss functions when varying this respective parameter and keeping
        all others constant at the value of the found optimum (blue dot).
        In the cases of (B-F), we can see that a minimum was achieved and thus the parameters could
        be estimated.
        However, for the case of the damping constant $\lambda$ in (A), we see that the upper bound
        is open.
        This suggests that our model could be reduced with regard to this parameter.
        We have exemplified the values for radii $r_i$ and growth rates $\mu_i$ with values of the
        first cell.
        The remaining plots can be found in the supplementary material in
        section~\ref{sec:supplement-parameter-profiles}.
    }
    \label{fig:parameter-estimates-single-step}
\end{figure}

@@

%###################################################################################################
% EXCLUDE THIS FOR NOW
% \section{Plastic Deformations}
% 
% \begin{figure}
%     \centering
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/0000000023.png}\\
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/angles.pdf}
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/endpoints.pdf}
%     \caption{TODO}
%     \label{fig:amir}
% \end{figure}

@@

%###################################################################################################
\section{Parameter Estimation}
\label{sec:supplement-parameter-profiles}
%TODO {explain profiles}
\begin{figure}
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-5.pdf}
    \caption{Parameter estimation of growth rates for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement-growth-rates}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-5.pdf}%
    \caption{Parameter estimation of radii for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement-radii}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]
        {docs/source/_static/performance/computation-time-with-initial-agents.pdf}
    \includegraphics[width=0.49\textwidth]{docs/source/_static/performance/flamegraph.pdf}
    \caption{TODO}
    \label{fig:performance}
\end{figure}
